\chapter{Pressupost}\label{chapter:pressupost}

This TFG project has been developed jointly with the GPI team. The budget presented is divided in Activities. Each Activity corresponds to an specific task, and the division has been done according to the equipment and staff needed to develop each tasks. In this budget are considered not only the activities developed in this project scope, but also the activities that are required to perform this project development. 

The Activities that had been taken into account are:
\begin{description}[font=\normalfont\textsl]
\item[Activity 1: Recording I.] Captures done using cones as a pattern.
\item[Activity 2: Recording II.] Captures done using a chessboard as a pattern.
\item[Activity 3: Undistortion.] Test the different undistortion algorithms.
\item[Activity 4: Registration, warping and blending.] This Activity includes all the algorithms and methods tested in this TFG project scope and are directly related to the Arcol project.
\item[Activity 5: Documentation.] Additional activity that includes all the tasks done outside the Arcol project scope -TFG writing, additional tests, etc.-.

\end{description}

Each Activity summarized cost is the following:

\begin{table}[H]
\begin{tabular}{l l r r r}
&Activity&Equipment&Workers&Subtotal\\
\hline\hline
1&Cone recording&197.06 \euro{}&290.00 \euro{}&487.06 \euro\\
2&Chessboard recording&205.83 \euro{}&290.00 \euro{}&495.83 \euro \\
3&Undistortion&46.70 \euro{}&1,030.00 \euro{}&1,076.70 \euro\\
4&Registration. warping and blending&442.00 \euro{}&21,000.00 \euro{}&21,442.00 \euro\\
5&Documentation&66.00 \euro{}&3,800.00 \euro{}&3,866.00 \euro\\[0.3cm]
& & &  \textbf{TOTAL} & \textbf{27.367,59\euro }
\end{tabular}
\end{table}

Each activity detailed costs can be found in Appendix~\ref{app:budget}. This Appendix also contains each equipment detailed amortization and each worker salary.


